High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 overall.tex
minor fixes to save 3-4 lines.

Currently 20 instances of the PanDA Broker are deployed on 4 Titan DTNs, with
5 instances per DTN\@. Each broker submits and manages the execution of 15 to
300 ATLAS jobs, one job for each Titan worker node, and a theoretical maximum
concurrent use of 96,000 cores. Since November 2015, PanDA Brokers have
operated only in backfill mode, without a defined time allocation, and
running at the lowest priority on Titan. Therefore, ATLAS contributed to an
increase of Titan's overall utilization.

>>>>

Currently 20 instances of the PanDA Broker are deployed on 4 DTNs, with
5 instances per DTN\@. Each broker submits and manages the execution of 15 to
300 jobs, one job for each Titan worker node, and a theoretical maximum
concurrent use of 96,000 cores. Since November 2015, PanDA Brokers have
operated only in backfill mode, without a defined time allocation, and
running at the lowest priority on Titan. Therefore, ATLAS contributed to an
increase of Titan's utilization.
